\cvsection{Projects}

\begin{cventries}

  \cventry
    {Python, Flask, React}
    {Nintendo 64 ROM Hack: Harvest Moon}
    {Palo Alto, CA}
    {Dec. 2018 - Present}
    {
      \begin{cvitems}
        \item {Located and extracted hidden values describing game state from a ROM using system calls on a concurrently running process.}
        \item{Created a React dashboard that polls a Flask backend to display the current values as the game is played.}
      \end{cvitems} 
    }
    
  \cventry
    {C}
    {Heap Allocator}
    {Palo Alto, CA}
    {March 2018}
    {
      \begin{cvitems}
        \item {Implemented an implicit heap allocator and an explicit heap allocator with custom malloc, realloc, and free functions.}
        \item {Augmented a test harness by adding methods for validating a heap structure after each call to the explicit or implicit allocator.}
      \end{cvitems}
    }

  \cventry
    {MongoDB, Express.js, AngularJS, Node.js, HTML, CSS}
    {Photo Sharing Application}
    {Palo Alto, CA}
    {May 2018 - June 2018}
    {
      \begin{cvitems}
        \item {Developed a single page web application for sharing, commenting on, and favoriting photos.}
        \item {Adhered to a MVC architecture and included session management with the notion of a user being signed in.}
      \end{cvitems} 
    }

  \cventry
    {NumPy, Python}
    {Sequence Aligner}
    {South Bend, IN}
    {Aug. 2016 - Dec. 2016}
    {
      \begin{cvitems}
        \item {Implemented dynamic programming algorithms Needleman-Wunsch and Smith-Waterman for sequence alignment.}
        \item {Delivered three public presentations on the mathematical foundations of pairwise and multiple sequence alignment algorithms.}
      \end{cvitems} 
    }
    
\end{cventries}