\cvsection{Research}
\begin{cventries}
    
  \cventry
    {Research under Euan Ashley, Stanford University}
    {Analysis of Variant Calling using Graph-Based Reference Genomes}
    {Palo Alto, CA}
    {June 2017 - Present}
    {
      \begin{cvitems}
        \item {Developing a pipeline for simulating variants into existing human genomes to create a better ground truth for variant identification.}
        \item {Benchmarking the performance of variant callers against linear and graph-based reference genomes for variants of different sizes.}
      \end{cvitems}
    }
    
  \cventry
    {Research under Imon Banerjee, Stanford University}
    {Detection of Prostate Lesions using an Efficient Neural Network}
    {Palo Alto, CA}
    {April 2018 - Present}
    {
      \begin{cvitems}
        \item {Created a model that outputs a probability map of pixel tumor character by downsampling images through layers of convolution and max pooling and then upsampling them through convolutional transpose layers and max unpooling using Pytorch.}
        \item {Improved lesion detection and unified models by performing shape-based alignment of images from three different MRI modalities.}
        \item {Preparing for publication.}
      \end{cvitems} 
    }

  \cventry
    {Research under Dennis Wall, Stanford University}
    {Cluster Validation for Autism Subtypes}
    {Palo Alto, CA}
    {Sept. 2017 - Dec. 2017}
    {
      \begin{cvitems}
        \item {Analyzed soft k-means clustering results generated using a Generalized Low Rank Model with logistic loss on autism phenotype data.}
        \item {Tracked the movement of individuals between clusters as the number of clusters increased to assess their biological meaningfulness.}
        \item {Visually presented the significant findings of the analysis using a Jupyter notebook built on the existing analysis pipeline.}
      \end{cvitems}
    }
    
\end{cventries}
